Can money buy happiness?

### 2022-04-29 draft2.Rmd
commit LETS GOOOOOOOOOOOO

```{r}
labels <- sprintf(
  "<strong>%s</strong><br/> %s",
  healthy_data_2$City, healthy_data_2$country) %>%
  lapply(htmltools::HTML)

@@

```{r}
GDPP_hours <- healthy_data_2 %>% 
ggplot( aes(x = GDPPC, y = `Hours Worked`)) +
  geom_point(color = "#3C1518") +
  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
       caption = "Data from: ADD LATER",
       x = "GDP per capita (USD)",
       y = "Hours Worked (Weekly)",
       color = "") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "#FFE5B4",
                                colour = "gray",
                                size = 0.5,
                                ),
        plot.title = element_text(size = 0.05))

ggplotly(GDPP_hours,
         width = 800,
         height = 430,
         tooltip = c("text", 
                     "x",
                     "City")) 
```

@@

```{r}
options(scipen=999)

ggplot(healthy_data_2, aes(y = fct_reorder(country, GDPPC), x = GDPPC, color = `Happiness levels(Country)`)) +
  geom_point() +
  labs(title = "Gross Domestic Product per Capita by Country and Happiness Level",
       caption = "Data from: ADD LATER",
       x = "GDP per capita (USD)",
       y = "",
       color = "Happiness Level 
       (1-10 scale)") +
  theme(plot.title = element_text(hjust = 1)) +
  theme_classic() +
  scale_color_gradient(high = "#FFD25A", low = "black")
```

>>>>

```{r, fig.alt = "World map showing 44 cities used in the analysis"}
labels <- sprintf(
  "<strong>%s</strong><br/> %s",
  healthy_data_2$City, healthy_data_2$country) %>%
  lapply(htmltools::HTML)

@@

```{r}
GDPP_hours <- healthy_data_2 %>% 
ggplot( aes(x = GDPPC, y = `Hours Worked`, fill = `City`)) +
  geom_point(color = "#3C1518") +
  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
       caption = "Data from: ADD LATER",
       x = "GDP per capita (USD)",
       y = "Hours Worked (Weekly)",
       color = "") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "#FFE5B4",
                                colour = "gray",
                                size = 0.5,
                                ),
        plot.title = element_text(size = 0.05))

ggplotly(GDPP_hours,
         width = 800,
         height = 430,
         tooltip = c("text", 
                     "x",
                     "y",
                     "City")) 
```

@@

```{r, fig.alt = "Graph showing gross domestic product (GDP) per capita by country and happiness level. Country is mapped on the y-axis and GDP per capita is mapped on the y-axis. Switzerland, Ireland, and the United States had the highest GDP per capita and also had high reported happiness levels. Countries with higher GDP per capita tend to have higher happiness levels"}
options(scipen=999)

ggplot(healthy_data_2, aes(y = fct_reorder(country, GDPPC), x = GDPPC, color = `Happiness levels(Country)`)) +
  geom_point() +
  labs(title = "GDP per Capita by Country and Happiness Level",
       caption = "Data from: Healthy Lifestyle Cities Report 2021, IMF World Economic Outlook",
       x = "GDP per capita (USD)",
       y = "",
       color = "Happiness Level 
       (1-10 scale)") +
  theme(plot.title = element_text(hjust = 0)) +
  theme_classic() +
  scale_color_gradient(high = "#FFD25A", low = "black")
```
